## Algorithm Quality
### Reliability
(ref:tab-mean-reliability-flanker) Reliability of different algorithms - Flanker Task
```{r tab-mean-reliability-flanker, tab.cap=paste("(ref:tab-mean-reliability-flanker)")}
knit_print(table_mean_reliability_flanker)
```

(ref:tab-mean-reliability-nback) Reliability of different algorithms - Nback Task

```{r tab-mean-reliability-nback, tab.cap=paste("(ref:tab-mean-reliability-nback)")}
knit_print(table_mean_reliability_nback)
```

(ref:tab-mean-reliability-switching) Reliability of different algorithms - Switching Task

```{r tab-mean-reliability-switching, tab.cap=paste("(ref:tab-mean-reliability-switching)")}
knit_print(table_mean_reliability_switching)
```

### Homogeneity
(ref:tab-mean-homogeneity-flanker) Homogeneity of different algorithms - Flanker Task
```{r tab-mean-homogeneity-flanker, tab.cap=paste("(ref:tab-mean-homogeneity-flanker)")}
knit_print(table_mean_homogeneity_flanker)
```

(ref:tab-mean-homogeneity-nback) Homogeneity of different algorithms - Nback Task

```{r tab-mean-homogeneity-nback, tab.cap=paste("(ref:tab-mean-homogeneity-nback)")}
knit_print(table_mean_homogeneity_nback)
```

(ref:tab-mean-homogeneity-switching) Homogeneity of different algorithms - Switching Task

```{r tab-mean-homogeneity-switching, tab.cap=paste("(ref:tab-mean-homogeneity-switching)")}
knit_print(table_mean_homogeneity_switching)
```

### Correlation with manually extracted latencies
(ref:tab-mean-manualcor-flanker) Correlation with manually extracted latencies - Flanker Task
```{r tab-mean-manualcor-flanker, tab.cap=paste("(ref:tab-mean-manualcor-flanker)")}
knit_print(table_mean_manualcor_flanker)
```

(ref:tab-mean-manualcor-nback) Correlation with manually extracted latencies - Nback Task

```{r tab-mean-manualcor-nback, tab.cap=paste("(ref:tab-mean-manualcor-nback)")}
knit_print(table_mean_manualcor_nback)
```

(ref:tab-mean-manualcor-switching) Correlation with manually extracted latencies - Switching Task

```{r tab-mean-manualcor-switching, tab.cap=paste("(ref:tab-mean-manualcor-switching)")}
knit_print(table_mean_manualcor_switching)
```

### Effect sizes
(ref:tab-mean-effsize-flanker) Effect size for the age effect - Flanker Task
```{r tab-mean-effsize-flanker, tab.cap=paste("(ref:tab-mean-effsize-flanker)")}
knit_print(table_mean_effsize_flanker)
```

(ref:tab-mean-effsize-nback) Effect size for the age effect - Nback Task

```{r tab-mean-effsize-nback, tab.cap=paste("(ref:tab-mean-effsize-nback)")}
knit_print(table_mean_effsize_nback)
```

(ref:tab-mean-effsize-switching) Effect size for the age effect - Switching Task

```{r tab-mean-effsize-switching, tab.cap=paste("(ref:tab-mean-effsize-switching)")}
knit_print(table_mean_effsize_switching)
```
